---
title: "simpleRegress"
author: "Irene Garcia"
date: "Fall 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Introduction 

We are comparing the variables chest and neck of a bear to see what variable is better at determining length. 


## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

Neck as a variable for determining a bears length had adjusted r square score of 0.7476.

The scatter plot shows that neck size goes up, length does as well as is a good predictor of length.

## now predict the length of a bear who has a neck of 17, 22 and 26


```{r}
new <- data.frame(NECK=c(17,22,26))
predict(simp,new)
predict(simp,new,se.fit=TRUE,interval = "prediction")

```

## Numerical Summary 


```{r}
cor(bears$LENGTH,bears$NECK)
```
## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).

```{r}
simp <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(simp)
summary.lm(simp)
```

Chest as a variable for determining a bears length had adjusted r square of 0.7869

The scatter plot shows that chest size goes up, length does as well, thus necks size is a good indicator.

## Numerical Summary 


```{r}st
cor(bears$LENGTH,bears$CHEST)
```

The correlation coefficient 

## Conclusion 

Chest had adjust r squared score of 0.7869 while neck had an adjust r squared score of 0.7476


Chest is a better predictor of length because the adjusted r-squared of the fit for chest was larger than neck. 